### 2019-04-04 tii/tex/abstract.tex
Update intro & abstract.

\begin{abstract}[S U M M A R Y]

In large-scale data-parallel analytics, shuffle, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large overhead. Due to the dependency constraints, execution of those descendant tasks could be delayed by logy shuffles.
To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
{\color{blue}
During the shuffle optimization process, we propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model. 
The FRQ model quantifies the utilization of resources and predicts the execution time of each phase of computing jobs. 
We use the FRQ model to analyze DAG frameworks and evaluate the SCache shuffle optimization by mathematics.
}
By extracting and analyzing shuffle dependencies prior to the actual task execution, SCache can adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node. 
Meanwhile, SCache takes full advantage of the system memory to accelerate the shuffle process. 
% {\color{red}
% We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
% Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
% }
{\color{blue}
We have implemented SCache as the external shuffle service and co-scheduler on both Apache Spark and Apache Hadoop MapReduce. The performance of SCache has been evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average. On Apache Hadoop MapReduce, SCache optimizes end-to-end Terasort completion time by $15\%$.
}
\end{abstract}

>>>>

\begin{abstract}

In large-scale data-parallel analytics, shuffle, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large overhead. Due to the dependency constraints, execution of those descendant tasks could be delayed by logy shuffles.
To reduce shuffle overhead, we present \textit{SCache}, an open source plug-in system that particularly focuses on shuffle optimization. 
By extracting and analyzing shuffle dependencies prior to the actual task execution, SCache can adopt heuristic pre-scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance load on each node. 
Meanwhile, SCache takes full advantage of the system memory to accelerate the shuffle process. 
% {\color{red}
% We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
% Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
% }
{\color{blue}
We also propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model to analyze DAG frameworks and evaluate the SCache shuffle optimization. 
The FRQ model quantifies the utilization of resources and predicts the execution time of each phase of computing jobs. 
% We use the FRQ model to analyze DAG frameworks and evaluate the SCache shuffle optimization by mathematics.
}
{\color{blue}
We have implemented SCache on both Apache Spark and Apache Hadoop MapReduce. The performance of SCache has been evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average. On Apache Hadoop MapReduce, SCache optimizes end-to-end Terasort completion time by $15\%$.
}
\end{abstract}

### 2019-04-04 tii/tex/intro.tex
Update intro & abstract.

\begin{figure}
	\centering
	\includegraphics
		[width=1\linewidth]
		{fig/workflow}
	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
	\label{fig:workflow}
\end{figure}

\section{Introduction}\label{sec:introduction}
Recent years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
Most of them define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce, lineage of resilient distributed datasets (RDDs) in Spark, vertices and edges in Dryad and Tez, etc.
Despite the differences among data-intensive frameworks, their communication is always structured as a shuffle phase,  which takes place between successive computation stages. 
Such shuffle phase places a significant burden for both the disk and network I/O, thus heavily affecting the end-to-end application performance. 
For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for $33\%$ of the job completion time on average, and up to $70\%$ in shuffle-heavy jobs \cite{managing}.

{\color{blue}
Various efforts of performance optimization have been made among computing frameworks, both at the software and hardware levels \cite{sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous, yviquel2018cluster, kaitoua2014hadoop, wasi2017comprehensive, zhang2018simpo, chen2013tiled}. However, the shuffle phase is often poorly optimized in practice.
}
% {\color{red}
% Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{sync, babu, tachyon, pacman, quincy, delay, ibrahim2012maestro, sharma2012mrorchestrator}, 
% the shuffle is often poorly optimized in practice.
% }
% take over shuffle
%shuffle characteristic
In particular, we observe that one major deficiency lies in the lack of fine-grained, coordinated management among different system resources.
%In the current practice, the shuffle phase is often split into two parts --- \textit{shuffle read} and \textit{shuffle write}. 
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
Such task aggregation together with the coarse-grained scheduling effectively simplifies task management.
However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
%The map task in Figure \ref{fig:workflow} well explains such deficiency: the I/O resource allocated to the stage is always idle during the computation time, and the computation/memory resource is totally wasted during the shuffle write attached to it, and vice versa.

Moreover, the shuffle read phase introduces all-to-all communication pattern across the network, and such network I/O procedure is also poorly coordinated.
Note that the shuffle read phase starts fetching data only after the corresponding reduce task starts.
Meanwhile, the reduce tasks belonging to the same execution phase are scheduled at the same time by default. 
As a result, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
Such synchronized network communication causes a burst demand for network I/O, which in turn greatly enlarges the shuffle read completion time. 
To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier, such as "slow-start" from Hadoop MapReduce.
However, such early-start is by no means a panacea. 
This is because the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.

%In one word, existing solutions suffer from either inefficient use of network I/O, or a waste of computational resources (i.e., CPU and memory) caused by task pre-launching.

@@

{\color{blue}
To analyze resources scheduling strategies as mentioned above, we propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model. The FRQ model quantifies computing and I/O resources and visualizes the resources scheduling strategies of DAG frameworks in the time dimension. We use the FRQ model to assist in analyzing the deficiencies of resources scheduling and optimize it. 
The FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
According to the above five parameters and the scheduling strategy of the DAG framework, the FRQ model is able to predict the execution time of each phase of a computing job. 
Taking Apache Hadoop MapReduce as a simple DAG computing example, we model each phase of the computing by the FRQ model, including Map, Shuffle, and Reduce.
By revealing the relationships between the various phases, the FRQ model assists us in discovering the irrationality of resource scheduling during computing.
% I/O resources in the map phase are not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
% This situation will be amplified in shuffle-heavy tasks.
}

Can we efficiently optimize the data shuffling without significantly changing DAG frameworks?
In this paper, we answer this question in the affirmative with S(huffle)Cache, an open source\footnote{https://github.com/frankfzw/SCache} plug-in system which provides a shuffle-specific optimization for different DAG computing frameworks.
Specifically, SCache takes over the whole shuffle phase from the underlying framework by providing a cross-framework API for both shuffle write and read.
SCache's effectiveness lies in the following two key ideas.
First, SCache decouples the shuffle write and read from both map and reduce tasks.
Such decoupling effectively enables fine-grained resource management and better multiplexing between the computational and I/O resources.
In addition, SCache pre-schedules the reduce tasks \emph{without launching} them and pre-fetches the shuffle data. 
% for the reduce tasks.
Such pre-scheduling and pre-fetching effectively overlap the network transfer time, desynchronize the network communication, 
and avoid the extra early allocation of slots.
%In this paper, we introduce S(huffle)Cache, an plugin system to remove shuffle latency for DAG frameworks. SCache takes over the management of shuffle and I/O resources to acheive a fine granularity scheduling of tasks. In addition, SCache pre-schedules the reduce tasks without launching them and perform shuffle data pre-fetch to break the synchronization of shuffle fetch. In order to provide a general optimization for different DAG frameworks, SCache decouple the shuffle process from computing and  provide a cross-frameworks API for shuffle write and read.

@@

Another challenge is the \textit{in-memory data management}. 
To prevent shuffle data touching the disk, SCache leverages extra memory to store the shuffle data. 
% However, the memory is a precious resource for DAG computing. 
To minimize the reserved memory while maximizing the performance gain, we propose two constraints: all-or-nothing and context-aware (Section \ref{memorymanage}).
%The memory management scheme follows these two contraints to switch shuffle data blocks on and off reserved memory.

% {\color{red}
% We have implemented SCache and a customized Apache Spark \cite{apachespark}. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster. We conduct basic test GroupByTest. We also evaluate Terasort \cite{spark-tera} benchmark and standard workloads like TPC-DS \cite{tpcds} for multi-tenant modeling. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied application scenarios. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average.
% }

{\color{blue}
We have implemented SCache on both Apache Spark \cite{apachespark} and Hadoop MapReduce. We have also designed a performance model called FRQ model to analyze the shuffle optimization of SCache and predict the execution time of each phase of a computing job. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop. On Apache Spark, we conduct a basic test - \textit{GroupByTest}. We also evaluate the system with Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling. On Apache Hadoop, we focus on Terasort benchmark. In a nutshell, SCache can eliminate explicit shuffle time by at most $89\%$ in varied applications. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark. On Apache Hadoop, SCache optimizes end-to-end Terasort completion time by $15\%$.
}

>>>>

\section{Introduction}\label{sec:introduction}
Recent years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
{\color{blue}
According to a MapReduce trace analysis from Facebook, the shuffle phase accounts for $33\%$ of the job completion time on average, and up to $70\%$ in shuffle-heavy jobs \cite{managing}.
The shuffle phase is crucial and heavily affecting the end-to-end application performance.
Most of the popular frameworks define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce, lineage of resilient distributed datasets (RDDs) in Spark, vertices and edges in Dryad and Tez, etc.
Despite the differences among data-intensive frameworks, the shuffle phase is always essential as communication between successive computation stages.
}

{\color{blue}
Various efforts of performance optimization have been made among computing frameworks, both at the software and hardware levels \cite{sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous, yviquel2018cluster, kaitoua2014hadoop, wasi2017comprehensive, zhang2018simpo, chen2013tiled}. However, the shuffle phase is often poorly optimized in practice.
In particular, we observe that one major deficiency lies in the coupled scheduling among different system resources.
}
%In the current practice, the shuffle phase is often split into two parts --- \textit{shuffle read} and \textit{shuffle write}. 
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
{\color{blue}
Such task aggregation together with the coupled scheduling effectively simplifies task management.
}
However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
%The map task in Figure \ref{fig:workflow} well explains such deficiency: the I/O resource allocated to the stage is always idle during the computation time, and the computation/memory resource is totally wasted during the shuffle write attached to it, and vice versa.

Moreover, the shuffle read phase introduces all-to-all communication pattern across the network, and such network I/O procedure is also poorly coordinated.
Note that the shuffle read phase starts fetching data only after the corresponding reduce task starts.
Meanwhile, the reduce tasks belonging to the same execution phase are scheduled at the same time by default. 
As a result, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
Such synchronized network communication causes a burst demand for network I/O, which in turn greatly enlarges the shuffle read completion time. 
To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier, such as "slow-start" from Hadoop MapReduce.
% However, such early-start is by no means a panacea. 
% This is because the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
{\color{blue}
However, such early-start has several deficiencise.
First, the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
Second, the early-start can not fully overlap the shuffle phases and the descendent stage. Due to the shuffle phases are coupled with the reduce phases and the size of slots is limited, only parts of reduce tasks can be early-start. 
Last but not least, it is hard to find the optimal time to begin the early-start. If too early, the descendent stages are not ready to output enough intermediate data for the shuffle. If too late, the idle network resource is wasted.
}
\begin{figure}
	\centering
	\includegraphics
		[width=1\linewidth]
		{fig/workflow}
	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
	\label{fig:workflow}
\end{figure}
%In one word, existing solutions suffer from either inefficient use of network I/O, or a waste of computational resources (i.e., CPU and memory) caused by task pre-launching.

@@

Can we efficiently optimize the data shuffling without significantly changing DAG frameworks?
In this paper, we answer this question in the affirmative with S(huffle)Cache, an open source\footnote{https://github.com/frankfzw/SCache} plug-in system which provides a shuffle-specific optimization for different DAG computing frameworks.
Specifically, SCache takes over the whole shuffle phase from the underlying framework by providing a cross-framework API for both shuffle write and read.
SCache's effectiveness lies in the following two key ideas.
First, SCache decouples the shuffle write and read from both map and reduce tasks.
Such decoupling effectively enables more flexible resource management and better multiplexing between the computational and I/O resources.
In addition, SCache pre-schedules the reduce tasks \emph{without launching} them and pre-fetches the shuffle data. 
% for the reduce tasks.
Such pre-scheduling and pre-fetching effectively overlap the network transfer time, desynchronize the network communication, 
and avoid the extra early allocation of slots.
%In this paper, we introduce S(huffle)Cache, an plugin system to remove shuffle latency for DAG frameworks. SCache takes over the management of shuffle and I/O resources to acheive a fine granularity scheduling of tasks. In addition, SCache pre-schedules the reduce tasks without launching them and perform shuffle data pre-fetch to break the synchronization of shuffle fetch. In order to provide a general optimization for different DAG frameworks, SCache decouple the shuffle process from computing and  provide a cross-frameworks API for shuffle write and read.

@@

Another challenge is the \textit{in-memory data management}. 
To prevent shuffle data touching the disk, SCache leverages extra memory to store the shuffle data. 
% However, the memory is a precious resource for DAG computing. 
To minimize the reserved memory while maximizing the performance gain, we propose two constraints: all-or-nothing and context-aware (Section \ref{impl}).
%The memory management scheme follows these two contraints to switch shuffle data blocks on and off reserved memory.

% {\color{red}
% We have implemented SCache and a customized Apache Spark \cite{apachespark}. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster. We conduct basic test GroupByTest. We also evaluate Terasort \cite{spark-tera} benchmark and standard workloads like TPC-DS \cite{tpcds} for multi-tenant modeling. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied application scenarios. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average.
% }
{\color{blue}
We also propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model. The FRQ model quantifies computing and I/O resources and visualizes the resources scheduling strategies of DAG frameworks in the time dimension. We use the FRQ model to assist in analyzing the deficiencies of resources scheduling and optimize it. 
% The FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
% According to the above five parameters and the scheduling strategy of the DAG framework, the FRQ model is able to predict the execution time of each phase of a computing job. 
% Taking Apache Hadoop MapReduce as a simple DAG computing example, we model each phase of the computing by the FRQ model, including Map, Shuffle, and Reduce.
By revealing the relationships between the various phases, the FRQ model assists us in discovering the irrationality of resource scheduling during computing. (Section \ref{model}).
% I/O resources in the map phase are not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
% This situation will be amplified in shuffle-heavy tasks.
}

{\color{blue}
We have implemented SCache on both Apache Spark \cite{apachespark} and Hadoop MapReduce. 
% We have also designed a performance model called FRQ model to analyze the shuffle optimization of SCache and predict the execution time of each phase of a computing job. 
The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop. On Apache Spark, we conduct a basic test - \textit{GroupByTest}. We also evaluate the system with Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling. On Apache Hadoop, we focus on Terasort benchmark. In a nutshell, SCache can eliminate explicit shuffle time by at most $89\%$ in varied applications. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark. On Apache Hadoop, SCache optimizes end-to-end Terasort completion time by $15\%$.
}
